%------------------------
% Resume Template
% Author : Ome Tiwari
% Github : https://github.com/xtroon
% License : MIT
%------------------------

\documentclass[a4paper,10pt]{article}
\usepackage{lmodern}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[colorlinks=true, urlcolor=black]{hyperref}



\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\vspace{3pt}

\textbf{{\Huge Ome Tiwari}} &
\href{mailto:ometiwari.ai@gmail.com}{ometiwari.ai@gmail.com}
\textbar\ 
+91 8114491829 \\

{\small\bfseries CSE Undergraduate | Full-Stack Developer} &
\underline{\href{https://xtroon.vercel.app}{Portfolio}}
\textbar\ 
\underline{\href{https://leetcode.com/u/omtiwari0/}{LeetCode}}
\textbar\ 
\underline{\href{https://github.com/xtroon}{GitHub}}
\textbar\ 
\underline{\href{https://www.linkedin.com/in/ometiwari-ai/}{LinkedIn}} \\

\end{tabular*}

%-----------EDUCATION-----------------
\section{ \textbf{Education}}
\vspace{5pt}

\resumeSubHeadingListStart

\resumeSubheading
{MBM University}{Jodhpur, Rajasthan}
{Bachelor of Engineering in Computer Science; CGPA: 7.94/10}
{Aug 2024 - Jul 2028}
\vspace{-5pt}

\item {\normalsize \textbf{Relevant Coursework:} Data Structures \& Algorithms, Database Management Systems, Object-Oriented Programming, Computer Networks}

\resumeSubHeadingListEnd

\vspace{-5pt}

%-----------SKILLS-----------------
\section{\textbf{Skills Summary}}
\vspace{5pt}

\resumeSubHeadingListStart

\resumeSubItem{Languages}{~~~~~~~Python, C, C++, JavaScript (ES6)}

\resumeSubItem{Frontend}{~~~~~~~~~React.js, HTML5, CSS3, Tailwind CSS}

\resumeSubItem{Backend}{~~~~~~~~~~Node.js, Express.js, REST APIs, WebSocket}

\resumeSubItem{Databases}{~~~~~~~~MongoDB, PostgreSQL, MySQL}

\resumeSubItem{Tools}{~~~~~~~~~~~~~~~Git, GitHub, Postman, Vercel, Firebase, Supabase, JWT Authentication}

\resumeSubItem{Core Concepts}{~Client-Server Architecture, Authentication, RESTful APIs, WebSocket Communication}


\resumeSubHeadingListEnd
\vspace{0pt}



%-----------Experience-----------------
\section{\textbf{Experience}}
\vspace{5pt}
  \resumeSubHeadingListStart
\resumeSubheading
{\mbox{\href{https://drive.google.com/file/d/1Ft0DEokZVvmM-lrBns6iLHZNaBr_1lM0/view?usp=sharing}{\color{black}Binary29}}}
{Nov 2025 - Feb 2026}
{Software Development Intern (Full-Stack)}
{Hybrid}
    \vspace{-4pt}
    \resumeItemListStart
        \item Developed a \textbf{full-stack} e-commerce platform for \textbf{Swadeshika} using Next.js, Tailwind CSS, and responsive frontend architecture.
        \item Designed and integrated RESTful APIs using Node.js and Express.js to streamline inventory management for \textbf{100+ organic products.}
        \item Implemented JWT-based authentication and scalable MySQL schemas to enable secure user management and \textbf{role-based access control.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

\vspace{-5pt}

%-----------PROJECTS-----------------
\section{\textbf{Projects}}
\vspace{5pt}
\resumeSubHeadingListStart

\item
\textbf{NearSwap} $|$ \emph{React Native, Node.js, Firebase Authentication, Firebase Cloud Messaging (FCM), Supabase}
\hfill
\href{https://nearswap.netlify.app/}{\underline{Live}}

\vspace{-6pt}

\resumeItemListStart
\item Developed a cross-platform marketplace application using React Native and Expo, facilitating item exchange among 50+ students within the college community.
\item Implemented secure user authentication and onboarding workflows using Firebase Authentication.
\item Enhanced user engagement through Firebase Cloud Messaging (FCM) by enabling real-time push notifications for marketplace activities.
\resumeItemListEnd


\vspace{-2pt}

\item
\textbf{Real-Time Chat Application} $|$ \emph{HTML, CSS, JavaScript, Node.js, Express.js, WebSocket}
\hfill
\href{https://realtime-chat-application-8u95.onrender.com}{\underline{Live}} $|$
\href{https://github.com/xtroon/Realtime-Chat-Application}{\underline{GitHub}}

\vspace{-6pt}

\resumeItemListStart
\item Developed a browser-based chat application enabling seamless communication between users through WebSocket technology.
\item Engineered a Node.js and Express.js backend to manage concurrent client connections and real-time message broadcasting.
\item Validated application scalability and low-latency performance through live testing with 20+ concurrent users.
\resumeItemListEnd


\vspace{-2pt}

\item
\textbf{Image Download Extension} $|$ \emph{JavaScript, HTML, CSS, Chrome Extension API}
\hfill
\href{https://github.com/xtroon/Image-Downloader-Extension}{\underline{GitHub}}

\vspace{-6pt}

\resumeItemListStart
\item Built a Chrome extension capable of detecting and downloading images from web pages through automated extraction workflows.
\item Utilized Chrome Extension APIs to automate image extraction and download workflows.
\item Built a lightweight and user-friendly interface to improve browsing productivity.
\resumeItemListEnd


\resumeSubHeadingListEnd
\vspace{0pt}





%-----------Awards-----------------
\section{ \textbf{Achievements}}
\vspace{5pt}
\begin{description}[font=$\bullet$]

\item {\textbf{Solved 500+ algorithmic problems} across 
\textbf{LeetCode} and 
\textbf{CodeChef}, demonstrating strong proficiency in Data Structures, Algorithms, and problem solving.}
\vspace{-2pt}

\item {Recognized as a \textbf{National Finalist} in the 
{National Entrepreneurship Challenge (NEC)} organized by 
\textbf{E-Cell, IIT Bombay}. \href{https://drive.google.com/file/d/1Ywirt-1Focep9TYrMrswJX-rUCcVo8ma/view}{[\underline{Certificate}]}}
\vspace{-2pt}

\item {Completed the 
\textbf{Meta Frontend Developer Certification}, specializing in responsive web design, modern frontend architecture.\href{https://www.coursera.org/account/accomplishments/verify/ZA9L4SC3QXDX}{[\underline{Certificate}]}}

\end{description}

\vspace{-2pt}


\end{document}
